Multi-frequency Radio Continuum Emission of Dust-free Red Giant Mass Outflows

### 2013-04-01 draft_03/draft.tex
1st upload of evla draft

Although studies of wind-scattered UV and optical line profiles have provided clues to the mass-loss rates and radial distribution of the mean and turbulent velocity fields, the thermal structure remains poorly constrained. In the UV, the source function is very sensitive to electron temperature (i.e. $S_{\nu} \propto e^{-h\nu /kT}$) and so a localized hot plasma component in a dynamic atmosphere can completely dominate the temporally and spatially averaged emission and not reflect the global mean value. At radio wavelengths however, the source function is thermal and is just the Rayleigh-Jeans tail of the Planck function, which is linear in electron temperature (i.e. $S_{\nu} = {2kT\nu ^2 /c^2}$) and so should give a more appropriate estimate of the thermal radial wind structure. It is this value that controls the atomic level populations and ionization that feed into UV spectroscopic analyses. This value is also needed to quantify the implied thermal heating supplied to the  wind by the unknown driving source/sources, and thus derive constraints on potential mass loss mechanisms.

@@

\begin{deluxetable}{ccc}
\tabletypesize{\scriptsize}
\tablecaption{Some properties of our red giant sample.}
\tablehead{	\colhead{}		       				& 
			\colhead{$\alpha$ Boo}				&
			\colhead{$\alpha$ Tau}				}
\startdata
Spectral Type 				& K2 III  & K5 III  \\
Effective Temperature (K)	& $4294 \pm 30$  & $3970 \pm 49$ \\
Angular Diameter (mas)		& $21.0 \pm 0.2$ & $20.2 \pm 0.3$ \\
Wind Temperature (K)		& $\sim 10,000$  & $< 10,000$  \\
Wind Terminal Velocity & $\sim$ 40 km s$^{-1}$ & $\sim$ 30 km s$^{-1}$ \\
Semi-empirical model	& \cite{1985pssl.proc..351D} & \cite{1999MNRAS.302...37M}
\enddata
\tablecomments{Effective temperatures and photospheric diameters are taken from \cite{1993AA...270..315D}.}

@@

\begin{deluxetable*}{Ccccc}
\tabletypesize{\scriptsize}
%\tablecolumns{6} 
%\tablewidth{0pt} 
\tablecaption{Compilation of Previous $\alpha$ Boo and $\alpha$ Tau Observations ($\le 250$ GHz)}
\tablehead{							            &
    \colhead{Frequency}		       				& 
			\colhead{Date}						&
			\colhead{Flux Density}				&
          	\colhead{Source} 			\\
												&
	\colhead{(GHz)}								&
	\colhead{}									&
    \colhead{(mJy)}		        				& 
    \colhead{}			         				}
\startdata
$\alpha$ Boo (K2 III) &4.9  & 1983 Jan 21 & $0.39 \pm 0.13$ & \cite{1986AJ.....91..602D} \\
&4.9  & 1983 May 20 & $0.26 \pm 0.08$ & \cite{1986AJ.....91..602D} \\
&4.9  & 1983 Dec 26 & $\le 0.18(3\sigma)$ & \cite{1986AJ.....91..602D} \\
&4.9  & 1984 Mar 17 & $0.24 \pm 0.05$ & \cite{1986AJ.....91..602D} \\
&15 & 1984 Nov 6 & $0.68 \pm 0.09$ & \cite{1986AJ.....91..602D} \\
&22.5  & 1999 Jan 06  & $ 1.7 \pm 0.2$ & \cite{2011AA...533A.107D} \\
&43.3  & 1999 Jan 06 & $ 3.3 \pm 0.4$ & \cite{2011AA...533A.107D} \\
&43.3  & 2004 Jan 25 & $ 3.34 \pm 0.08$ & \cite{2011AA...533A.107D} \\
&86  & 1985 Nov  & $ 21.4 \pm 7.5$ & \cite{1986AA...164..227A} \\
&108.4  & 1997 Nov - 2000 Jun & $ 20.09 \pm 0.69$ & \cite{2005AJ....129.2836C} \\
&217.8 & 1997 Nov - 2000 Jun  & $ 83.5 \pm 1.71$ & \cite{2005AJ....129.2836C} \\
&250  & 1986 Dec - 1989 Mar  & $ 78 \pm 8$ & \cite{1994AA...281..161A} \\
\hline
\rule{0pt}{3ex}    $\alpha$ Tau (K5 III)	&4.9  & 1983 Jan 21 & $\le 0.27(3\sigma)$ & \cite{1986AJ.....91..602D} \\
&4.9  & 1984 Nov 6 & $\le 0.22(3\sigma)$ & \cite{1986AJ.....91..602D} \\
&5.0  & 1997 Sep 27 & $\le 0.07(3\sigma)$		& Brown \& Harper (priv. comm.) \\
&8.5  & 1997 Sep 27 & $0.28 \pm 0.03$ 		& Brown \& Harper (priv. comm.) \\
&14.9 & 1997 Sep 27 & $0.95 \pm 0.08$ 		& Brown \& Harper (priv. comm.) \\
&15 & 1984 Nov 6 & $0.60 \pm 0.1$ 		& \cite{1986AJ.....91..602D} \\
&108.4  & 1997 Nov - 2000 Dec & $ 13.97 \pm 1.46$ & \cite{2005AJ....129.2836C} \\
&217.82 & 1999 Sep - 2000 Dec  & $ 25.78 \pm 5.64$ & \cite{2005AJ....129.2836C} \\
&250  & 1986 Dec - 1987 Jan & $ 51 \pm 6$ & \cite{1994AA...281..161A} 
\enddata
\label{tab:tab4}
\end{deluxetable*}

\section{DISCUSSION}
\subsection{Spectral Energy Distribution of $\alpha$ Boo} \label{disc1}
The first definite detection of a single red giant at centimeter wavelengths was of $\beta$ Gem by \cite{1983ApJ...274L..77D}. Included in this study was a probable $3\sigma$ detection of $\alpha$ Boo and since then there has been only a small number of sporadic centimeter and millimeter observations of the star. In Table \ref{tab:tab3} we list the majority of these observations and plot their flux densities as a function of frequency in Figure \ref{fig:fig1}. We also include in this figure the chromosphere and wind models of \cite{1985pssl.proc..351D} which were based on the International Ultraviolet Explorer (IUE) Mg II k emission line and the overlap between the two models are represented by the green shaded area. At high frequencies the models predict the slope of the spectral energy distribution to be blackbody-like (i.e. $\sim \nu ^{2}$) as a result of the small density scale heights close to the star. At low frequencies however, the models predict the wind to have constant velocity, ionization and temperature and thus the slope  approaches the well known $\sim \nu ^{0.6}$ limit \citep{1975MNRAS.170...41W,1975AA....39..217O,1975AA....39....1P}. The paucity and, in some cases low S/N, of previous observations make it difficult to discern the validity of this model prior to our multi-frequency study of this star.

The peak flux density values listed in Table \ref{tab:tab3} for $\alpha$ Boo are also included in Figure \ref{fig:fig1} along with their $1\sigma$ rms errors. Our new data reveal significant deviations from the current existing semi-empirical model at both low and high frequencies (in this case below $\sim$ 8 GHz and above $\sim$ 25 GHz). At low frequencies this discrepancy may indicate that we are still sampling a region of the wind where it is still accelerating (i.e. it has not yet reached its terminal velocity) or may also be a manifestation of rapid wind cooling further out than that predicted in UV spectral analysis. Our highest frequency data points indicate a flux excess which is in agreement with previous higher frequency (i.e. mm-observations) observations. One notable exception to this high frequency flux excess are the two 43 GHz observations of \cite{2011AA...533A.107D} which are lower than our values by over 40\%. Such a level of chromospheric viability seems very high and would be unexpected from such supposedly inactive stars. Another possibility for the difference in values  is that the longer cycle times used by \cite{2011AA...533A.107D}, which was over double our value, may cause larger phase errors and thus lower final flux density values. Future high frequency observations may clarify this matter.

\subsection{Spectral Energy Distribution of $\alpha$ Tau} \label{disc2}
\\
d
\\
\\
zz
\\
\\
\\
\\
d
\\
\\
zz
\\
\\
\\
\\
d
\\
\\
zz
\\
\\
\\
\subsection{Contribution Functions?} \label{disc3}
\subsection{Mass loss e.g. Drake & Linskey ?} \label{disc4}
\subsection{Future Atmospheric Models e.g. Advection?} \label{disc5}

\begin{figure*}
\centering
\includegraphics[trim = 0mm 0mm 0mm 20mm, clip,scale=0.65, angle=90]{fig1.ps}
\\
\caption{Spectral energy distribution of $\alpha$ Boo for frequencies less than 250 GHz. Our new multi-frequency VLA observations which were mainly acquired over a few days in February 2011 are the blue circular data points and appear to be in disagreement with the existing chromospheric and wind models of \cite{1985pssl.proc..351D} which are shown in green. The red circles are the previous observations which were acquired sporadically over the past $\sim 25$ years.}
\label{fig:fig1}
\centering
\includegraphics[trim = 0mm 0mm 0mm 20mm, clip,scale=0.65, angle=90]{fig2.ps}
\\
\caption{Spectral energy distribution of $\alpha$ Tau for frequencies less than 250 GHz. All our new $\alpha$ Tau multi-frequency VLA observations (blue circular data points) were acquired in just two days in February 2011. The red circles are the previous observations which were acquired over many years. The green line is an existing hybrid chromosphere and wind model for the star.}
\label{fig:fig2}
\end{figure*}

>>>>

Although studies of wind-scattered UV and optical line profiles have provided clues to the mass loss rates and radial distribution of the mean and turbulent velocity fields, the thermal structure remains poorly constrained. In the UV, the source function is very sensitive to electron temperature (i.e. $S_{\nu} \propto e^{-h\nu /kT}$) and so a localized hot plasma component in a dynamic atmosphere can completely dominate the temporally and spatially averaged emission and not reflect the global mean value. At radio wavelengths however, the source function is thermal and is just the Rayleigh-Jeans tail of the Planck function, which is linear in electron temperature (i.e. $S_{\nu} = {2kT\nu ^2 /c^2}$) and so should give a more appropriate estimate of the thermal radial wind structure. It is this value that controls the atomic level populations and ionization that feed into UV spectroscopic analyses. This value is also needed to quantify the implied thermal heating supplied to the  wind by the unknown driving source/sources, and thus derive constraints on potential mass loss mechanisms.

@@

\begin{deluxetable}{ccc}
\tabletypesize{\scriptsize}
\tablecaption{Some properties of our red giant sample.}
\tablehead{	\colhead{}		       				& 
			\colhead{$\alpha$ Boo}				&
			\colhead{$\alpha$ Tau}				}
\startdata
Spectral Type 				& K2 III  & K5 III  \\
Effective Temperature (K)	& $4294 \pm 30$  & $3970 \pm 49$ \\
Angular Diameter (mas)		& $21.0 \pm 0.2$ & $20.2 \pm 0.3$ \\
Mass Loss Rate (M$_{\odot}$ yr$^{-1}$)		& 2$\times$10$^{-10}$ & 1.6$\times$10$^{-11}$ \\
Wind Temperature (K)		& $\sim 10,000$  & $< 10,000$  \\
Wind Terminal Velocity & $\sim$ 40 km s$^{-1}$ & $\sim$ 30 km s$^{-1}$ \\
Semi-empirical model	& \cite{1985pssl.proc..351D} & \cite{1999MNRAS.302...37M}
\enddata
\tablecomments{Effective temperatures and photospheric diameters are taken from \cite{1993AA...270..315D}. Mass loss rates are from \cite{1985pssl.proc..351D} and \cite{1998ApJ...503..396R}.}

@@

\begin{deluxetable*}{Ccccc}
\tabletypesize{\scriptsize}
%\tablecolumns{6} 
%\tablewidth{0pt} 
\tablecaption{Compilation of Previous $\alpha$ Boo and $\alpha$ Tau Observations ($\le 250$ GHz)}
\tablehead{							            &
    \colhead{Frequency}		       				& 
			\colhead{Date}						&
			\colhead{Flux Density}				&
          	\colhead{Source} 			\\
												&
	\colhead{(GHz)}								&
	\colhead{}									&
    \colhead{(mJy)}		        				& 
    \colhead{}			         				}
\startdata
$\alpha$ Boo (K2 III) &4.9  & 1983 Jan 21 & $0.39 \pm 0.13$ & \cite{1986AJ.....91..602D} \\
&4.9  & 1983 May 20 & $0.26 \pm 0.08$ & \cite{1986AJ.....91..602D} \\
&4.9  & 1983 Dec 26 & $\le 0.18(3\sigma)$ & \cite{1986AJ.....91..602D} \\
&4.9  & 1984 Mar 17 & $0.24 \pm 0.05$ & \cite{1986AJ.....91..602D} \\
&15.0 & 1984 Nov 6 & $0.68 \pm 0.09$ & \cite{1986AJ.....91..602D} \\
&22.5  & 1999 Jan 06  & $ 1.7 \pm 0.2$ & \cite{2011AA...533A.107D} \\
&43.3  & 1999 Jan 06 & $ 3.3 \pm 0.4$ & \cite{2011AA...533A.107D} \\
&43.3  & 2004 Jan 25 & $ 3.34 \pm 0.08$ & \cite{2011AA...533A.107D} \\
&86.0  & 1985 Nov  & $ 21.4 \pm 7.5$ & \cite{1986AA...164..227A} \\
&108.4  & 1997 Nov - 2000 Jun & $ 20.09 \pm 0.69$ & \cite{2005AJ....129.2836C} \\
&217.8 & 1997 Nov - 2000 Jun  & $ 83.5 \pm 1.71$ & \cite{2005AJ....129.2836C} \\
&250.0  & 1986 Dec - 1989 Mar  & $ 78 \pm 8$ & \cite{1994AA...281..161A} \\
\hline
\rule{0pt}{3ex}    $\alpha$ Tau (K5 III)	&4.9  & 1983 Jan 21 & $\le 0.27(3\sigma)$ & \cite{1986AJ.....91..602D} \\
&4.9  & 1984 Nov 6 & $\le 0.22(3\sigma)$ & \cite{1986AJ.....91..602D} \\
&5.0  & 1997 Sep 27 & $\le 0.07(3\sigma)$		& Brown \& Harper (priv. comm.) \\
&8.5  & 1997 Sep 27 & $0.28 \pm 0.03$ 		& Brown \& Harper (priv. comm.) \\
&14.9 & 1997 Sep 27 & $0.95 \pm 0.08$ 		& Brown \& Harper (priv. comm.) \\
&15.0 & 1984 Nov 6 & $0.60 \pm 0.1$ 		& \cite{1986AJ.....91..602D} \\
&108.4  & 1997 Nov - 2000 Dec & $ 13.97 \pm 1.46$ & \cite{2005AJ....129.2836C} \\
&217.8 & 1999 Sep - 2000 Dec  & $ 25.78 \pm 5.64$ & \cite{2005AJ....129.2836C} \\
&250.0  & 1986 Dec - 1987 Jan & $ 51 \pm 6$ & \cite{1994AA...281..161A} 
\enddata
\label{tab:tab4}
\end{deluxetable*}

\section{DISCUSSION}
\subsection{Results Versus Previous Observations} \label{disc1}
Prior to and during the early operation of the VLA, a small number of single dish radio observations reported the detection of flares from single red giants (e.g. \citealt{1981ApJ...245L..71B}). These transient radio events have never been re-observed however, even with more sensitive interferometers, suggesting that such detections were false (e.g. \citealt{1992MNRAS.254....1B}). The first definitive detection of thermal free-free emission from a single red giant at centimeter wavelengths was of $\alpha$ Boo at 6 cm \citep{1983ApJ...274L..77D,1986AJ.....91..602D}. Since then there has been a modest number of sporadic centimeter and millimeter observations of this star. In Table \ref{tab:tab3} we list the majority of these observations and plot their flux densities as a function of frequency in Figure \ref{fig:fig1}. In comparison to other single red giants, $\alpha$ Boo had been relatively well observed at radio wavelengths before this study, including detections in four VLA bands (i.e. Q, K, Ku, and C). No Ku band receivers were available during the commissioning phase of the VLA in early 2011 so we can compare three of our detections with previous ones.

Previous detections at 6 cm ranged from a 3$\sigma$ upper limit of 0.18 mJy to a 3$\sigma$ detection at 0.39 mJy. Our 6 cm value agrees to within $\sim$10$\%$ of the highest S/N (5$\sigma$) value of \cite{1986AJ.....91..602D}. There is no significant difference between our 1.3 cm value and that of \cite{2011AA...533A.107D}.
There is however a notable difference in flux density values at 0.7 cm  where \cite{2011AA...533A.107D} report values that are lower than ours by over 40\%. Such a level of chromospheric variability seems rather high and would be unexpected from such supposedly inactive stars. Another possibility for the difference in values is that the longer cycle time used by \cite{2011AA...533A.107D}, which was over double our value, may cause larger phase errors and thus lower final flux density values. Future high frequency VLA observations of $\alpha$ Boo will clarify this discrepancy at 0.7 cm but past detections at longer wavelengths appear to be in good agreement with our data.

Prior to this study, $\alpha$ Tau had only been detected at two VLA bands (i.e. X and Ku) and had never been detected at wavelengths longer than 3 cm due to its weakly ionized wind. The lack of a Ku measurement means that we can only compare the previous 3 cm detection of Brown $\&$ Harper (1997) to ours. We find that there is no significant difference between the two. Interestingly however, Brown $\&$ Harper (1997) failed to detect $\alpha$ Tau at 6 cm but placed a 3$\sigma$ upper limit of 0.07 mJy on its emission. In stark contrast to this, we were able to detect the star at 6 cm with a flux density over two times greater than this value. This hint of variability at long wavelengths can only again be confirmed with future high S/N observations.

\subsection{Existing Atmospheric Models} \label{disc2}
One of the most important diagnostic features indicating mass outflows in late type stars are the blue shifted absorption components present in the Mg {\textsc{ii}} h and k resonance lines. Figure \ref{fig:fig1} shows the predicted radio spectrum from the chromosphere and wind models of \cite{1985pssl.proc..351D}, which were based on the Mg {\textsc{ii}} k 2796 $\rm{\AA}$ emission line taken with the the International Ultraviolet Explorer. Both of Drake's models predict the wind to reach its terminal velocity of 40 km s${}^{-1}$ at $\sim$ 2 R${}_{\star}$ and have a broad temperature plateau with T $\approx$ 8,000 K between 1.2 and $\sim$ 13 R${}_{\star}$ with a cooler region further out. At high frequencies the models predict the slope of the spectral energy distribution to be blackbody-like (i.e. $\sim \nu ^{2}$) as a result of the small density scale heights close to the star. At low frequencies however, the models predict the wind to have constant velocity, ionization and temperature and thus the slope approaches the well known $\sim \nu ^{0.6}$ limit \citep{1975MNRAS.170...41W,1975AA....39..217O,1975AA....39....1P}. The paucity and, in some cases low S/N, of previous observations made it difficult to discern the validity of this model prior to our multi-frequency study of $\alpha$ Boo. Our new data reveal significant deviations from the current existing semi-empirical model at both low and high frequencies (in this case below $\sim$ 8 GHz and above $\sim$ 25 GHz). At high frequencies our VLA data indicates a flux excess which is in agreement with previous higher frequency (i.e. mm-observations) observations. The  discrepancy at low frequencies may indicate that we are still sampling a region of the wind where it is still accelerating (i.e. it has not yet reached its terminal velocity) or may also be a manifestation of rapid wind cooling further out than that predicted in UV spectral analysis. We will discuss these possibilities in the following sections.

In Figure \ref{fig:fig2} we plot the expected thermal radio continuum spectrum produced by the semi-empirical 1-D  chromospheric model of \cite{1999MNRAS.302...37M} embedded in the wind model of \cite{1998ApJ...503..396R}. The McMurry model includes a transition region and reaches a maximum temperature of 10$^{5}$ K at 1.2 R$_{\star}$. Beyond this we assume an outflow with a constant temperature of 8,000 K reaching a terminal velocity of 30 km s$^{-1}$ at 3 R$_{\star}$. The combination of these models predicts an excess of radio emission at high frequencies (i.e. $>$ 30 GHz) but does a good job in reproducing the VLA fluxes below 30 GHz. The VLA, Institut de Radioastronomie Millim\'{e}trique (IRAM) 30 m-telescope and Berkeley Illinois Maryland Association (BIMA) continuum fluxes confirm that this model predicts a flux excess at high frequencies. One possible explanation for this is that the inner atmosphere contains extensive cooler gas than that predicted by the 1-D static chromospheric model of McMurry. This scenario agrees with the findings of \cite{1994ApJ...423..806W} who conclude that cool regions exist close to the stellar surface with large filling factors (i.e. a thermally bifurcated CO-mosphere). For $\alpha$ Boo there is a strong hint that the transition frequency between wind and chromosphere occurs  at about 8.5 GHz but for $\alpha$ Tau, with its low mass loss rate giving rise to a low wind opacity, this is harder to distinguish. There is a small hint that this may occur at 6 cm and a higher S/N detection at 13 cm would confirm this.

We also include the predicted radio spectrum from the theoretical Alfv\`{e}n wave driven outflow model for $\alpha$ Tau \citep{1989AcA....39...51K} in Figure \ref{fig:fig2}. This model is based on a larger than now expected mass-loss rate for the star (i.e 6.3$\times$10$^{-9}$ M{$_{\odot$}} yr$^{-1}$) and predicts a fully ionized outflow. As the radio opacity is proportional to n$\rm{_{e}}$n$\rm{_{ion}}$ this model greatly over-predicts the actual radio flux density. The same result is to be expected from the Alfv\`{e}n wave model of $\alpha$ Boo \citep{1988AcA....38..107K}.

\begin{figure*}
\centering
\includegraphics[trim = 0mm 0mm 0mm 20mm, clip,scale=0.65, angle=90]{fig1.ps}
\\
\caption{Spectral energy distribution of $\alpha$ Boo for frequencies less than 250 GHz. Our new multi-frequency VLA observations which were mainly acquired over a few days in February 2011 are the blue circles and appear to be in disagreement with the existing chromospheric and wind models of \cite{1985pssl.proc..351D}. The overlap between the two models are represented by the green shaded area. The red circles are previous observations which were acquired sporadically over the past $\sim 25$ years with the ``old" VLA, IRAM and BIMA.}
\label{fig:fig1}
\centering
\includegraphics[trim = 0mm 0mm 0mm 20mm, clip,scale=0.65, angle=90]{fig2.ps}
\\
\caption{Spectral energy distribution of $\alpha$ Tau for frequencies less than 250 GHz. All our new $\alpha$ Tau multi-frequency VLA observations (blue circles) were acquired in just two days in February 2011. The red circles are the previous observations which were acquired over many years. The green line is an existing hybrid chromosphere and wind model for the star.}
\label{fig:fig2}
\end{figure*}

\subsection{Radio Spectral Indices from Mass Outflows} \label{disc3}
For a thermal source which has a constant electron density distribution, its radio emission has a well defined spectral index $\alpha$ ($\rm{S}_{\nu} \propto \nu ^{\alpha}$). For an optically thick homogeneous plasma $\alpha$ follows the Rayleigh-Jeans tail of the Planck function (i.e. $\alpha = +2$), while for an optically thin homogeneous plasma $\alpha = -0.1$. However, the electron density in the mass outflow region of a star is not constant as a function of radius and usually varies by many orders of magnitude. It has been shown \citep{1975MNRAS.170...41W,1975AA....39..217O,1975AA....39....1P} that the expected radio spectrum from such a mass outflow region varies as $\nu ^{0.6}$, where a spherically symmetric isothermal mass outflow with a uniform velocity is assumed. If we do not make the simplified assumption of an isothermal, constant velocity mass outflow but instead assume that the electron density and temperature profiles vary as a function of distance from the star $r$, and have the form $n_{e} \propto r^{-p}$ and $T_{e} \propto r^{-n}$ respectively, where $p > 1.5$ then

\begin{figure}
\includegraphics[trim = 0mm 0mm 0mm 10mm, clip,scale=0.385,angle=90]{fig3.ps}
\caption{Radio spectra for $\alpha$ Boo and $\alpha$ Tau, together with the best fit straight lines to their long wavelength flux densities and the resulting spectral indices.}
\label{fig:fig3}
\end{figure}

\begin{equation}
\alpha = \frac{4p -6.2 -0.6n}{2p-1-1.35n}.
\label{eq:eq1}
\end{equation}
\citep[e.g.][]{1987ApJ...312..813S}. Thus, by assuming either a constant velocity (i.e. $p=2$) or an isothermal outflow (i.e. $n=0$), we can easily estimate the power-law decay of either the temperature or velocity profile, respectively.

The radio spectra for both stars are shown in Figure \ref{fig:fig3}, together with the straight lines that were fitted to the long wavelength flux densities by minimizing the chi-square error statistic. For $\alpha$ Boo a straight line with $S_{\nu} \propto \nu ^{1.05 \pm x}$ fits the four longest wavelength data points well. This spectral index is larger than the 0.8 value obtained by \cite{1986AJ.....91..602D} whose value was based on a shorter wavelength (2 cm) value and a mean value of four low S/N measurements at 6 cm. $\alpha$ Tau was found to have a larger spectral index and a straight line with $S_{\nu} \propto \nu ^{1.58 \pm x}$ best fitted the three longest wavelength data points. This value is in agreement with \cite{1986AJ.....91..602D} who report a value $\ge 0.84$ and is lower than the value of 2.18 that can be derived from the shorter wavelength data provided by Brown \& Harper (priv. Comm.). These new spectral indices were then used in conjunction with Equation \ref{eq:eq1} to obtain the density and temperature coefficients listed in Table \ref{tab:tab5}.

\begin{figure}
\includegraphics[trim = 0mm 0mm 0mm 10mm, clip,scale=0.385,angle=90]{fig4.ps}
\caption{Predicted effective radius (dashed lines) as a function of wavelength for $\alpha$ Boo and $\alpha$ Tau. Points corresponding to our long wavelength VLA measurements are also shown.  At the same radio wavelengths the less ionized mass outflow of $\alpha$ Tau results in a smaller effective radius than $\alpha$ Boo.}
\label{fig:fig4}
\end{figure}

For an isothermal, constant velocity wind, Equation \ref{eq:eq1} implies $\alpha$ = 0.6. The fact that our derived values are substantially larger implies at least one of the assumptions regarding the wind's properties are false. A common explanation in the literature for spectral indices larger than 0.6 is that the wind is still accelerating in the region where the radio emission is emanating from. If this is also the case here, then the density obeys a power-law falloff with coefficients listed in column 3 of Table \ref{tab:tab5}. This assumption is reasonable at short wavelengths where the majority of the radio emission is expected to emanate within the wind's acceleration zone, but at  long VLA wavelengths (i.e. between 6 and 20 cm) this assumption might be false and we may indeed be sampling the wind very close to its terminal velocity.

\begin{deluxetable}{cccc}
\tabletypesize{\scriptsize}
\tablecaption{Radio Spectral Indices for $\alpha$ Boo and $\alpha$ Tau along with their density and temperature coefficients.}
\tablehead{	\colhead{}		       				& 
			\colhead{Spectral}				&
			\colhead{Density}				&
			\colhead{Temperature}				\\
			\colhead{Star}		       				& 
			\colhead{index $\alpha$ }				&
			\colhead{coefficient $p$ }				&
			\colhead{coefficient $n$ }				}

\startdata
$\alpha$ Boo				& 1.05  & 2.71 & 1.65\\
$\alpha$ Tau			& 1.58 & 5.50 & 1.92
\enddata
\label{tab:tab5}
\end{deluxetable}

To investigate this matter further,  we estimate the effective radius of the radio emitting region per wavelength using the Drake model for $\alpha$ Boo and the hybrid McMurry and Robinson model for $\alpha$ Tau. We follow the approach used by \cite{1977ApJ...212..488C} and assume that the radio emission at any wavelength emanates from a surface at effective optical depth $\tau _{\rm{eff}}=$1/3. Since the radio free-free opacity increases at longer wavelengths (i.e. $\kappa \propto \lambda ^{2.1}$) the optical depth along a line of sight into the stellar outflow also increases at longer wavelengths. This implies that the effective radius (i.e. the radius where $\tau = \tau _{\rm{eff}}$) will increase with longer wavelengths and will be greater for outflows with higher ionization densities as $\tau \propto \int \lambda ^{2.1}n_{\rm{ion}}n_{\rm{e}} dr$.

The higher degree of ionization in the mass outflow of $\alpha$ Boo in comparison to $\alpha$ Tau makes a substantial difference to the size of the stars effective radius as can be seen in Figure \ref{fig:fig4}. At 6, 13, and 20 cm the effective radius of $\alpha$ Boo is predicted to be 1.6, 2.8, and 3.7 $R_{\star}$ while is only $\sim 1.1 R_{\star}$ at 6 and 13 cm for $\alpha$ Tau. \cite{1998ApJ...503..396R} predict that $\alpha$ Tau's wind does not reach its terminal velocity until 3 $R_{\star}?$ while the transition region in the model of \cite{1999MNRAS.302...37M} begins at 1.2 $R_{\star}$, so it appears highly unlikely that even our longest wavelength VLA measurements of $\alpha$ Tau sample its outer wind. For $\alpha$ Boo however, \cite{1985pssl.proc..351D} predicts that the wind has reached its terminal velocity by $\sim$ 2 $R_{\star}$ so based on this model, our longest VLA measurements probable sample its wind at (or very close to) its terminal velocity. Our spectral index would then indicate that the wind is cooling as it expands with a constant velocity and has a temperature coefficient of 1.65.

\subsection{Analytical Advection Model for $\alpha$ Boo's Wind} \label{disc4}
A failure of the existing atmospheric model for $\alpha$ Boo is that is overestimates the radio fluxes at long VLA wavelengths as clearly shown in Figure \ref{fig:fig1}. If these wavelengths are indeed sampling the wind at its terminal velocity then a reason for this overestimation may be that the wind is cooling closer in than that predicted by the model. The main mechanism for this cooling would be wind expansion \citep{2011ASPC..448..691O} and would cause lower electron densities than those predicted by the existing model due to larger recombination rates. To investigate this possibility further we adjusted the existing model to include a temperature power-law falloff of the form
\begin{equation}
T_{e}(r)= T_{e}(r_{1})\left(\frac{r_{1}}{r}\right)^{1.65},
\label{eq:eq2}
\end{equation}
where $r_{1}$ is just an arbitrary distance from the star and the temperature coefficient is that obtained from our new VLA data (see Table \ref{tab:tab5}). To calculate the new $n_{\rm{e}}$ and $n_{\rm{ion}}$ densities in the wind regime where this temperature falloff occurs, we used the analytical expression of \cite{1986ApJ...306..605G} to calculate the hydrogen ionization fraction, $x_H$. In doing so we need to make a number of assumptions about the wind properties from $r_{1}$ onwards.
\begin{itemize}
\item We assume a conserved mass outflow i.e. $n_{H}(r)=C/r^2$ where $n_{H}$ is the total hydrogen number density and $C$ is a constant proportional to the ratio of the mass loss rate divided by the terminal velocity. For $\alpha$ Boo, $C = 1.5 \times 10^{32} $ cm$^{-1}$.
\item We assume that all ionization processes cease.
\item We consider only radiative recombination of H and include the temperature variation of the recombination coefficient $\alpha ^{b}$ which excludes captures to the n=1 level \citep{1978ppim.book.....S}.
\item We assume a constant heavy ion fraction, $x_{hi}=10^{-4}$.
\end{itemize}
Using these assumptions it can be shown that 
\begin{equation}
x_H(r)= \frac{x_{H}(r_1)x_{hi}e^{-I}}{x_{hi}+x_{H}(r_1)(1 - e^{-I})}
\label{eq:eq3}
\end{equation}
where
\begin{equation}
I = 2.38 \times 10^{-3} \left[\left( \frac{r_{1}}{r}\right)^{-0.19} -1 \right], \ \rm{and} \ \  r \geq r_{1}.
\label{eq:eq4}
\end{equation}
If we alter the existing Drake model so that it now has a narrower temperature  plateau of $T_e = 10,000$ K between 1.2 and 2.3 $R_{\star}$, a temperature profile given by Equation \ref{eq:eq2} and a density profile governed by Equation \ref{eq:eq3} beyond 2.3 $R_{\star}$, then we get a  good agreement with our new long wavelength VLA data as shown in Figure \ref{fig:fig1}.

Encouraging as it is that such a simple analytical model can reproduce values close to the observed radio fluxes at long wavelengths, it must be stressed that this \textit{hybrid} model is just a first order approximation. It still does not reproduce the radio fluxes at wavelengths shorter than $\sim$ 3 cm and therefore a new atmospheric model is still required that can reproduce all the observed fluxes. To do so, the non-trivial task of simultaneously solving the non-local radiative transfer equation and atomic rate equations which include advection will be required.

\subsection{Ionized Mass Loss Rates} \label{disc5}
